Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-03-04 RR_manuscript/Draft_RR.Rmd
:memo: - Draft_RR ready

## Operationalizing speech

@@

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations (e.g. the atypical *a blue banana* vs the typical *a yellow banana*)?
More specifically, we are interested in the acoustic profile of referring expressions made up of a noun and an adjective modifier.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy [@grice1975logic].
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective *yellow* to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

@@

Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
Each trial was repeated twice, yielding a total of 70 trials ($(15 \times 10 \times 10) \times 2$) per participant and a grand-total of 2100 observations ($70 \times 30$ participants), of which 900 ($15 \times 2 \times 30$ participants) were the experimentally relevant trials.
The recordings of the second sentence prompt of each trial make up the speech dataset given to the analysis teams.

@@

The present study examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results.
We are further interested in which factors affect the researchers' final results.

@@

This project involves a series of steps (X-X):

1. We will recruit independent groups of researchers to analyze the data.
2. We will give researchers access to the speech corpus and let them analyze the data as they see fit.
3. We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
4. We will evaluate the variation among the different analyses.
5. Lastly, we will collaboratively produce the final manuscript.

We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X).
The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent groups of scientists.

## Step 1: Recruitment and Initial Survey of Analysts

<!-- TODO: add materials link and mailing lists -->
The initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accessibility to potential analysts (LINK).
The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we refer to single researcher or small teams as "analysis teams".

Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each data set (see sample size justification below).
We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
<!-- TODO: add link to informed consent form -->
All analysts will sign a consent (ethics) document (LINK).

<!-- TODO: add citation to ECO RR -->
To identify the minimal sample size, we followed the method in [ECO RR].
The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
Ideally, the 95% credible interval (CrI) of $\tau^2$ should not include 0 (i.e. the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistics:

@@

## Step 2: Primary Data Analyses

@@

## Step 3: Peer Reviews of Analyses

@@

## Step 4: Evaluate variation

@@

## Step 6: Collaborative Write-Up of Manuscript

>>>>

## Operationalizing speech {#s:operspeech}

@@

The data set given to the analysis teams comes from a study that investigated whether speakers acoustically modify utterances to signal typicality of noun/adjective combinations in referring expressions such as  *a blue banana* (atypical) vs *a yellow banana* (typical).
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy [@grice1975logic].
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective *yellow* to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

@@

Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
Each trial was repeated twice, yielding a total of 70 trials ($(15 \times 10 \times 10) \times 2$) per participant and a grand-total of 2100 observations ($70 \times 30$ participants), of which 900 ($15 \times 2 \times 30$ participants) were the experimentally relevant trials.
The recordings of the second sentence prompt of each trial make up the speech data set given to the analysis teams.
The teams were asked to answer the same questions as the study that generated the data set: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
\comment[id=SC]{Need transition here.}

@@

The present study examines the extent to which subjective choices by different researchers analyzing the same speech data set affect the reported results.
As outlined in Section \@ref(s:operspeech), researchers are faced with a large set of analytical choices when investigating a multidimensional signal such as speech.
Not only must they choose appropriate statistical models and inferential criteria, but also identify relevant measures and their operationalisation and transformation, and the temporal domain(s) from within which these measures are to be taken.
\highlight[id=SC, comment={I need help completing this sentence...}]{The ... makes up the ideal testing ground for ...}
We will take on a meta-analytical approach to assess (i) the variability of the reported effects, and (ii) and how analytical and demographic factors affect the researchers' final results.

@@

This project involves the following five phases:

1. \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data.
2. \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
3. \textsc{Review}: We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
4. \textsc{Meta-analysis}: We will evaluate the variation among the different analyses.
5. \textsc{Write-up}: Lastly, we will collaboratively produce the final manuscript.

<!-- TODO: project timeline -->
We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take \highlight{XX months (Table X).}
The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent analysis teams.

## Phase 1: Recruitment of analysts and initial survey

<!-- TODO: add materials link and mailing lists -->
The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project (LINK) and a short pre-recorded slide show that summarizes the study and research question (LINK).
The project will be advertised via social media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include \highlight{LIST OF LISTS}, and via word of mouth.
The target population is active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in a relevant discipline.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer to single researcher or small teams as "analysis teams".

Recruitment for this project is ongoing but we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
<!-- TODO: add link to informed consent form -->
All analysts will sign a consent (ethics) document (LINK).

<!-- TODO: add citation to ECO RR -->
To identify the minimal sample size, we followed the method in \highlight{[ECO RR]}.
The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
Ideally, the 95% credible interval (CrI) of $\tau^2$ should not include 0 (i.e. the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistics:

@@

## Phase 2: Primary Data Analyses

@@

## Phase 3: Peer Reviews of Analyses

@@

## Phase 4: Evaluate variation

@@

## Phase 6: Collaborative Write-Up of Manuscript

### 2021-03-04 RR_manuscript/Draft_RR.tex
:memo: - Draft_RR ready

\hypertarget{operationalizing-speech}{%
\subsection{Operationalizing speech}\label{operationalizing-speech}}

@@

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations (e.g.~the atypical \emph{a blue banana} vs the typical \emph{a yellow banana})?
More specifically, we are interested in the acoustic profile of referring expressions made up of a noun and an adjective modifier.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

@@

Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
Each trial was repeated twice, yielding a total of 70 trials (\((15 \times 10 \times 10) \times 2\)) per participant and a grand-total of 2100 observations (\(70 \times 30\) participants), of which 900 (\(15 \times 2 \times 30\) participants) were the experimentally relevant trials.
The recordings of the second sentence prompt of each trial make up the speech dataset given to the analysis teams.

@@

The present study examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results.
We are further interested in which factors affect the researchers' final results.

@@

This project involves a series of steps (X-X):

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  We will recruit independent groups of researchers to analyze the data.
\item
  We will give researchers access to the speech corpus and let them analyze the data as they see fit.
\item
  We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
\item
  We will evaluate the variation among the different analyses.
\item
  Lastly, we will collaboratively produce the final manuscript.
\end{enumerate}

We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X).
The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent groups of scientists.

\hypertarget{step-1-recruitment-and-initial-survey-of-analysts}{%
\subsection{Step 1: Recruitment and Initial Survey of Analysts}\label{step-1-recruitment-and-initial-survey-of-analysts}}

The initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accessibility to potential analysts (LINK).
The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we refer to single researcher or small teams as ``analysis teams.''

Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each data set (see sample size justification below).
We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
All analysts will sign a consent (ethics) document (LINK).

To identify the minimal sample size, we followed the method in {[}ECO RR{]}.
The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
Ideally, the 95\% credible interval (CrI) of \(\tau^2\) should not include 0 (i.e.~the probability \(p\) that the 95\% CrI contains 0 should be less than 0.05).
The probability \(p\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistics:

@@

\hypertarget{step-2-primary-data-analyses}{%
\subsection{Step 2: Primary Data Analyses}\label{step-2-primary-data-analyses}}

@@

\hypertarget{step-3-peer-reviews-of-analyses}{%
\subsection{Step 3: Peer Reviews of Analyses}\label{step-3-peer-reviews-of-analyses}}

@@

\hypertarget{step-4-evaluate-variation}{%
\subsection{Step 4: Evaluate variation}\label{step-4-evaluate-variation}}

@@

\hypertarget{step-6-collaborative-write-up-of-manuscript}{%
\subsection{Step 6: Collaborative Write-Up of Manuscript}\label{step-6-collaborative-write-up-of-manuscript}}

>>>>

\hypertarget{s:operspeech}{%
\subsection{Operationalizing speech}\label{s:operspeech}}

@@

The data set given to the analysis teams comes from a study that investigated whether speakers acoustically modify utterances to signal typicality of noun/adjective combinations in referring expressions such as \emph{a blue banana} (atypical) vs \emph{a yellow banana} (typical).
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

@@

Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
Each trial was repeated twice, yielding a total of 70 trials (\((15 \times 10 \times 10) \times 2\)) per participant and a grand-total of 2100 observations (\(70 \times 30\) participants), of which 900 (\(15 \times 2 \times 30\) participants) were the experimentally relevant trials.
The recordings of the second sentence prompt of each trial make up the speech data set given to the analysis teams.
The teams were asked to answer the same questions as the study that generated the data set: \emph{Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?}
\comment[id=SC]{Need transition here.}

@@

The present study examines the extent to which subjective choices by different researchers analyzing the same speech data set affect the reported results.
As outlined in Section \ref{s:operspeech}, researchers are faced with a large set of analytical choices when investigating a multidimensional signal such as speech.
Not only must they choose appropriate statistical models and inferential criteria, but also identify relevant measures and their operationalisation and transformation, and the temporal domain(s) from within which these measures are to be taken.
\highlight[id=SC, comment={I need help completing this sentence...}]{The ... makes up the ideal testing ground for ...}
We will take on a meta-analytical approach to assess (i) the variability of the reported effects, and (ii) and how analytical and demographic factors affect the researchers' final results.

@@

This project involves the following five phases:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data.
\item
  \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
\item
  \textsc{Review}: We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
\item
  \textsc{Meta-analysis}: We will evaluate the variation among the different analyses.
\item
  \textsc{Write-up}: Lastly, we will collaboratively produce the final manuscript.
\end{enumerate}

We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take \highlight{XX months (Table X).}
The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent analysis teams.

\hypertarget{phase-1-recruitment-of-analysts-and-initial-survey}{%
\subsection{Phase 1: Recruitment of analysts and initial survey}\label{phase-1-recruitment-of-analysts-and-initial-survey}}

The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project (LINK) and a short pre-recorded slide show that summarizes the study and research question (LINK).
The project will be advertised via social media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include \highlight{LIST OF LISTS}, and via word of mouth.
The target population is active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in a relevant discipline.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer to single researcher or small teams as ``analysis teams.''

Recruitment for this project is ongoing but we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
All analysts will sign a consent (ethics) document (LINK).

To identify the minimal sample size, we followed the method in \highlight{[ECO RR]}.
The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
Ideally, the 95\% credible interval (CrI) of \(\tau^2\) should not include 0 (i.e.~the probability \(p\) that the 95\% CrI contains 0 should be less than 0.05).
The probability \(p\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistics:

@@

\hypertarget{phase-2-primary-data-analyses}{%
\subsection{Phase 2: Primary Data Analyses}\label{phase-2-primary-data-analyses}}

@@

\hypertarget{phase-3-peer-reviews-of-analyses}{%
\subsection{Phase 3: Peer Reviews of Analyses}\label{phase-3-peer-reviews-of-analyses}}

@@

\hypertarget{phase-4-evaluate-variation}{%
\subsection{Phase 4: Evaluate variation}\label{phase-4-evaluate-variation}}

@@

\hypertarget{phase-6-collaborative-write-up-of-manuscript}{%
\subsection{Phase 6: Collaborative Write-Up of Manuscript}\label{phase-6-collaborative-write-up-of-manuscript}}
